Kids PM Summary

### 2020-07-02 collinearity_exposure_analysis.Rmd
exposure analysis and data cleaning updates

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

>>>>

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period_7.5,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period_7.5,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

### 2020-07-02 exposure_covariate_associations.Rmd
exposure analysis and data cleaning updates

  analysis_data <- dataset %>% 
    filter(winter_id == 1 & treatment_assigned == "Placebo" & area == "WMT") %>% 
    group_by(area, home) %>% 
    distinct(home, .keep_all = TRUE) %>% 
    rename(analysis_covar = covar) %>% 
    ungroup() %>% 
    select(pm_mean_sampling_period, analysis_covar)

@@

  print(table(model.frame(analysis_results)$analysis_covar))
  #print(nobs(analysis_results))

@@

d39 <- analysis_function("sums_mean_sampling_period_5", "SUMs mean temperature")
d40 <- analysis_function("temp_perc_25_2level", "SUMs - % obs > 25 degrees C")
d41 <- analysis_function("temp_perc_27_2level", "SUMs - % obs > 27 degrees C")
d42 <- analysis_function("temp_perc_30_2level", "SUMs - % obs > 30 degrees C")
d43 <- analysis_function("sums_events_sampling_period", 
                         "Daily SUMs events - 5C temp increase in 20 min")

@@

####### Combine results to use in a table
table_data <- rbind(d1, d2, d3, d4, d5, d6,
                    d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18,
                    d19, d20, d21, d22,
                    d23, d24, d25, d26,
                    d27, d28, d29, d30,
                    d31, d32, d33, d34, d35, d36, d37, d38,
                    d39, d40, d41, d42, d43,
                    d44, d45,
                    d46, d47, d48, d49, d50, d51, d52, d53, d54, d55, d56,
                    d57, d58, d59, d60,
                    d61)

####### Print full table of results
kable(table_data, longtable = TRUE,
      caption = "Indoor PM2.5 (natural log transformed) and covariate associations") %>% 
   kable_styling(latex_options = "repeat_header") %>% 
   row_spec(0, bold = TRUE) %>% 
   pack_rows("Demographic variables", 1, 8) %>%
   pack_rows("Home characteristics", 9, 31) %>%
   pack_rows("Stove use", 32, 36) %>%
   pack_rows("Wood moisture content", 37, 40) %>%
   pack_rows("Indoor temperature and relative humidity", 41, 48) %>%
   pack_rows("Stove Use Monitors (SUMs) temperature", 49, 53) %>%
   pack_rows("Ambient data", 54, 55) %>%
   pack_rows("Home activities - Sum of all sampling days", 56, 70) %>%
   pack_rows("Stove grade", 71, 72) %>%
   footnote(c("PM2.5 = fine particulate matter", 
              "PM2.5 and all covariates have been averaged or summed to produce 1 observation per sampling period"))
```

>>>>

  analysis_data <- dataset %>% 
    filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
    group_by(area, home) %>% 
    distinct(home, .keep_all = TRUE) %>% 
    rename(analysis_covar = covar) %>% 
    ungroup() %>% 
    select(pm_mean_sampling_period, analysis_covar)

@@

  #print(table(model.frame(analysis_results)$analysis_covar))
  print(nobs(analysis_results))

@@

d39 <- analysis_function("sums_mean_sampling_period_5", "SUMs mean temperature")
d40 <- analysis_function("temp_perc_25_2level", "SUMs - % obs > 25 degrees C")
d41 <- analysis_function("temp_perc_27_2level", "SUMs - % obs > 27 degrees C")
d42 <- analysis_function("temp_perc_30_2level", "SUMs - % obs > 30 degrees C")
d43 <- analysis_function("sums_events_sampling_period_5", 
                         "SUMs events - 5C temp increase in 20 min")

@@

d62 <- analysis_function("ruca_code_3", "RUCA Code")

d63 <- analysis_function("sums_events_sampling_period_2.5", 
                         "SUMs events - 2.5C temp increase in 20 min")
d64 <- analysis_function("sums_events_sampling_period_7.5", 
                         "SUMs events - 7.5C temp increase in 20 min")

####### Combine results to use in a table
table_data <- rbind(d1, d2, d3, d4, d5, d6,
                    d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18,
                    d19, d20, d21, d22,
                    d23, d24, d25, d26,
                    d27, d28, d29, d30,
                    d31, d32, d33, d34, d35, d36, d37, d38,
                    d39, d40, d41, d42, d43,
                    d44, d45,
                    d46, d47, d48, d49, d50, d51, d52, d53, d54, d55, d56,
                    d57, d58, d59, d60,
                    d61, d62, d63, d64)

####### Print full table of results
kable(table_data, longtable = TRUE,
      caption = "Indoor PM2.5 (natural log transformed) and covariate associations") %>% 
   kable_styling(latex_options = "repeat_header") %>% 
   row_spec(0, bold = TRUE) %>% 
   pack_rows("Demographic variables", 1, 8) %>%
   pack_rows("Home characteristics", 9, 31) %>%
   pack_rows("Stove use", 32, 36) %>%
   pack_rows("Wood moisture content", 37, 40) %>%
   pack_rows("Indoor temperature and relative humidity", 41, 48) %>%
   pack_rows("Stove Use Monitors (SUMs) temperature", 49, 53) %>%
   pack_rows("Ambient data", 54, 55) %>%
   pack_rows("Home activities - Sum of all sampling days", 56, 70) %>%
   pack_rows("Stove grade", 71, 72) %>%
   pack_rows("RUCE Code", 73, 74) %>% 
   pack_rows("SUMs other", 75, 76) %>% 
   footnote(c("PM2.5 = fine particulate matter", 
              "PM2.5 and all covariates have been averaged or summed to produce 1 observation per sampling period"))
```

### 2020-07-02 exposure_models.Rmd
exposure analysis and data cleaning updates

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, income_3level, area, home,
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period))   
  select(-pm_mean_sampling_period) %>%

@@

When selecting data above, WMT has 63 observations
When use `na.exclude()` to only use complete data (what is needed for AIC selection),
the observations drops to 34. While there is only 7.5% missing data, it is spread
out enough that excluding it to have complete observations means we can only use
less than half for model selection. This would be a very biased version of model
selection to exclude that much data, which justifies multiple imputation to 
impute the 7.5% missing data and use that for model selection.
The missing observations are even more extreme for NN and AK.

@@

# Check % missing data
mean(is.na(selected_vars)) # 7.5% for WMT

@@

missing_summary <- complete_case %>% 
  group_by(area, wood_collect_2level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, wood_collect_2level, n, perc, total_n)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area, wood_collect_2level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, wood_collect_2level, n, perc, total_n)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 40,
                     method = c("polr", "logreg", "logreg", "logreg", "logreg",
                                "polr", "polr", "logreg", "logreg", "pmm",
                                "pmm", "polr", "logreg", "pmm"))

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_22may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_22may2020.rds"))

@@

# Can add "long" or "broad arguments
complete(imputed_data, "long")

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_22may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_22may2020.rds"))

>>>>

# Select analysis vars
selected_vars <- analysis_data %>% 
  filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period_7.5,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>%  
  select(-pm_mean_sampling_period)

@@

When selecting data above, WMT has 63 observations
When use `na.exclude()` to only use complete data (what is needed for AIC selection),
the observations drops to 27. While there is only 8.4% missing data, it is spread
out enough that excluding it to have complete observations means we can only use
less than half for model selection. This would be a very biased version of model
selection to exclude that much data, which justifies multiple imputation to 
impute the 8.4% missing data and use that for model selection.
The missing observations are even more extreme for NN and AK.

@@

# Check % missing data
mean(is.na(selected_vars)) # 8.4% for WMT

@@

missing_summary <- complete_case %>% 
  group_by(area, income_3level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, income_3level, n, perc, total_n)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area, income_3level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, income_3level, n, perc, total_n)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 40,
                     method = c("polr", "logreg", "logreg", "logreg", "logreg",
                                "polr", "polr", "logreg", "pmm",
                                "pmm", "pmm", "polr", "polr", "pmm"))

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_2july2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_2july2020.rds"))

@@

# Can add "long" or "broad" arguments
complete(imputed_data, "long")

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_2july2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_2july2020.rds"))

### 2020-07-02 manuscript_tables_figures.Rmd
exposure analysis and data cleaning updates

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
```

@@

num_funct_total("residents_under_five")
num_funct_area("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_area("home_bedrooms")
num_funct_total("pm_mean_sampling_period")
num_funct_area("pm_mean_sampling_period")
num_funct_total("pm_sample_interval")
num_funct_area("pm_sample_interval")
num_funct_total("moisture_closest")
num_funct_area("moisture_closest")
num_funct_total("temp_indoor_max")
num_funct_area("temp_indoor_max")
num_funct_total("rh_indoor_max")
num_funct_area("rh_indoor_max")
num_funct_total("mean_temp")
num_funct_area("mean_temp")
num_funct_total("amb_pm_24hr")
num_funct_area("amb_pm_24hr")
```

>>>>

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

num_funct_total("residents_under_five")
num_funct_area("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_area("home_bedrooms")
num_funct_total("pm_mean_sampling_period")
num_funct_area("pm_mean_sampling_period")
num_funct_total("pm_sample_interval")
num_funct_area("pm_sample_interval")
num_funct_total("moisture_closest")
num_funct_area("moisture_closest")
num_funct_total("temp_indoor_max")
num_funct_area("temp_indoor_max")
num_funct_total("rh_indoor_max")
num_funct_area("rh_indoor_max")
num_funct_total("mean_temp")
num_funct_area("mean_temp")
num_funct_total("amb_pm_24hr")
num_funct_area("amb_pm_24hr")
num_funct_total("sums_events_sampling_period_2.5")
num_funct_area("sums_events_sampling_period_2.5")
num_funct_total("sums_events_sampling_period_5")
num_funct_area("sums_events_sampling_period_5")
num_funct_total("sums_events_sampling_period_7.5")
num_funct_area("sums_events_sampling_period_7.5")
```

### 2020-07-02 merge_datasets.Rmd
exposure analysis and data cleaning updates

####### Format SUMs data to merge with analysis data below
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home, sampling_day) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 5, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(sums_events_sampling_day = sum(heat_event, na.rm = TRUE),
         sums_events_sampling_day_cat = cut(sums_events_sampling_day, 
                                            breaks = c(0, 2, 50),
                           labels = c("<2", "2+"),
                                 right = FALSE)) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(area:pm_rolling_20, sums_mean_winter:sums_mean_sampling_period,
         time_diff:sums_events_sampling_day_cat) %>% 
  arrange(area, home, sample_date) %>% 
  group_by(home) %>% 
  mutate(sums_events_sampling_period = mean(sums_events_sampling_day, na.rm = TRUE)) %>% 
  select(area, home, home_winter_id, sums_events_sampling_period) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

>>>>

####### Format SUMs data to merge with analysis data below
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home, sampling_day) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         # change temp in the following line
         temp_diff_check_2.5 = if_else(temp_diff >= 2.5, 1, 0),
         heat_event_2.5 = if_else(temp_diff_check_2.5 == 1 & lag(temp_diff_check_2.5) == 1, 0,
                              temp_diff_check_2.5),
         heat_event_2.5 = if_else(is.na(temp_diff_check_2.5), 1,
                              heat_event_2.5),
         temp_diff_check_5 = if_else(temp_diff >= 5, 1, 0),
         heat_event_5 = if_else(temp_diff_check_5 == 1 & lag(temp_diff_check_5) == 1, 0,
                              temp_diff_check_5),
         heat_event_5 = if_else(is.na(temp_diff_check_5), 1,
                              heat_event_5),
         temp_diff_check_7.5 = if_else(temp_diff >= 7.5, 1, 0),
         heat_event_7.5 = if_else(temp_diff_check_7.5 == 1 & lag(temp_diff_check_7.5) == 1, 0,
                              temp_diff_check_7.5),
         heat_event_7.5 = if_else(is.na(temp_diff_check_7.5), 1,
                              heat_event_7.5)) %>% 
  arrange(area, home, sample_date) %>% 
  group_by(area, home) %>% 
  mutate(sums_events_sampling_period_2.5 = sum(heat_event_2.5, na.rm = TRUE),
         sums_events_sampling_period_5 = sum(heat_event_5, na.rm = TRUE),
         sums_events_sampling_period_7.5 = sum(heat_event_7.5, na.rm = TRUE)) %>% 
  select(area, home, home_winter_id, 
         sums_events_sampling_period_2.5,
         sums_events_sampling_period_5,
         sums_events_sampling_period_7.5) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

### 2020-07-02 pm_summary.Rmd
exposure analysis and data cleaning updates

```{r}
# home that exceed PM guidelines
pm_guidelines <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm_mean_sampling_period > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```

@@

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=8}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 500) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

@@

```{r, fig.height=, fig.width=8}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    scale_y_log10() +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

@@

>>>>

```{r}
# homes that exceed PM guidelines
pm_guidelines <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  filter(pm_mean_sampling_period > 12) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines

pm_guidelines <- pm_clean %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  #group_by(area) %>% 
  mutate(total_obs = n()) %>% 
  filter(pm > 12) %>% 
  mutate(cutoff_obs = n(),
         cutoff_perc = cutoff_obs/total_obs*100) %>% 
  distinct(area, .keep_all = TRUE)
pm_guidelines

#Pm by different levels of covariates
pm_check <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(chimney_clean_3level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_check

# closer look at stove grade and PM
pm_stove_grade <- exposure_analysis_data_short %>%
  select(area, home, pm_mean_sampling_period, stove_grade_3level, 
         treatment_assigned, winter_id, home_winter_id) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(stove_grade_2level = fct_collapse(stove_grade_3level,
                                           "A" = "A",
                                           "C or F" = c("C", "F"))) %>% 
  group_by(stove_grade_2level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_stove_grade

model_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(area == "WMT") %>% 
  filter(home == "WMA300") %>% 
  distinct(home, .keep_all = TRUE)

check_model <- lm(log(pm_mean_sampling_period) ~ stove_grade_3level,
                  data = model_data)

summary(check_model)
```

@@

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=8}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 500) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

@@

```{r, fig.height=, fig.width=8}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

@@

```{r}
# check PM spikes
spikes_data <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  select(area, home, sampling_day, pm_mean_sampling_day, pm_mean_sampling_period,
         pm_spike_1000, pm_spike_2000, pm_spike_5000,
         income_3level, stove_grade_3level, chimney_clean_3level, home_floors_2level) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  group_by(area, home) %>% 
  distinct(area, home, sampling_day, .keep_all = TRUE) %>% 
  mutate(pm_spike_1000 = if_else(pm_spike_1000 == "Yes", 1, 0),
         pm_spike_2000 = if_else(pm_spike_2000 == "Yes", 1, 0),
         pm_spike_5000 = if_else(pm_spike_5000 == "Yes", 1, 0),
         spike_sum_1000 = sum(pm_spike_1000),
         spike_sum_2000 = sum(pm_spike_2000),
         spike_sum_5000 = sum(pm_spike_5000)) %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  mutate(spike_sum_1000 = as.factor(spike_sum_1000),
         spike_sum_1000 = fct_collapse(spike_sum_1000, "0" = "0",
                                       "1" = "1",
                                       "2" = "2",
                                       "3+" = c("3", "5"))) %>% 
  ungroup() %>% 
  arrange(area, home)

spikes_summary <- spikes_data %>% 
  mutate(spike_sum_1000 = as.factor(spike_sum_1000),
         spike_sum_1000 = fct_collapse(spike_sum_1000, "0" = "0",
                                       "1" = "1",
                                       "2" = "2",
                                       "3+" = c("3", "5"))) %>% 
  group_by(spike_sum_1000) %>% 
  summarize("N" = n(),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE), 
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE), 
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
spikes_summary

table(spikes_data$spike_sum_1000)
table(spikes_data$spike_sum_1000, spikes_data$stove_grade_3level)
```
